Augmentation of a Historical Harpsichord Keyboard Replica for Haptic-Enabled Interaction in Museum Exhibitions

### 2025-01-27 src/main.tex

\begin{acks}
 We acknowledge the invaluable contributions of
\begin{itemize}
\item
  Università di Bologna
  \begin{itemize}
  \item
    Alma Labor
    \begin{itemize}
    \item
      Massimiliano Fraulini and the staff of Alma Labor at the Università
      di Bologna for their 3D printing expertise and generosity with
      electronics equipment
    \end{itemize}
  \item
    Fisica Tecnica
    \begin{itemize}
    \item
      Maurzio Chendi Fabrizio Casarini, Giulio Severo and Barbara
      Costantini
    \end{itemize}
  \end{itemize}
\item
  Edinburgh
  \begin{itemize}
  \item
    uCreate
    \begin{itemize}    
    \item
      Simeon, Stuart, Millie, and Ruth of uCreate at the Univeristy of
      Edinburgh for their support with soldering facilities.
    \end{itemize}
  \item
    University of Edinburgh
    \begin{itemize}
    \item
      Richard Collins and the Digital Making Staff at the Edinburgh
      College of Art for 3D printing instruction and CNC support.
    \item
      Joe Hathaway of Digital Development at the College of Art for
      providing electronics components
    \item
      St Cecilia's Jenny Nex
    \end{itemize}
  \end{itemize}
\end{itemize}

>>>>

\begin{acks}
 We acknowledge the invaluable contributions of
\begin{itemize}
\item
  Università di Bologna
  \begin{itemize}
  \item
    \emph{Alma Labor}:
      Massimiliano Fraulini and the staff of Alma Labor at the Università
      di Bologna for their 3D printing expertise and generosity with
      electronics equipment
  \item
    \emph{Fisica Tecnica}: Maurzio Chendi, Fabrizio Casarini, Giulio Severo and Barbara
      Costantini    
  \end{itemize}
\item
  University of Edinburgh
  \begin{itemize}
  \item
    \emph{uCreate}:    
      Simeon, Stuart, Millie, and Ruth of uCreate at the Univeristy of
      Edinburgh for their support with soldering facilities.    
  \item
    \emph{Edinburgh College of Art}: Richard Collins and the Digital Making Staff at the Edinburgh
      College of Art for 3D printing instruction and CNC support. Digital Development Technician Joe Hathaway    
    \item  
      \emph{St Cecilia's}: Curator Dr. Jenny Nex
  \end{itemize}
\end{itemize}
